---
output: semantic.doc::semantic_document
---

```{r, echo = F, results = "hide"}
pacman::p_load(dplyr)
```


<!-- Menu -->
<div class="ui top attached menu">
  <a id="menu_link" class="item">
    <i class="sidebar icon"></i> Menu
  </a>
</div>
<!--   Menu end -->


<style type="text/css">
  h1, .h1, h2, .h2, h3, .h3 {
    margin-top: 50px;
  }
</style>


<div class="pusher">

<div id="settings" class="ui one column grid" style="display: none;">
<!--       Login Start -->
      <div class="column">
          <div class="ui segment">
              <h4>CLWRota API Login</h4>
          </div>
      </div>
</div>

<div id="itu">

<div class = "ui vertical teal inverted segment">

<br><br><br>

<h1 class = "ui centered header">
  Semantic UI Features
</h1>

<br><br><br>

</div>


<!-- https://bootsnipp.com/semanticui/snippets/featured/jumbotron-like-bootstrap -->
<div class="row">
  <div class="column padding-reset">
    <div class="ui huge message page grid">
      <h1 class="ui huge header">Hello, world!</h1>
      <p>This is a snippet for any type of website. It includes a call-to-action button and looks kind of like the jumbotron from Bootstrap. It does not require any additional CSS rules.</p>
      <a class="ui blue button">Learn more »</a>
    </div>
  </div>
</div>


<div class = "ui container">
<div class = "sixteen wide column">


## SOURCES

* [Codepen storange in JS and Semantic UI](https://codepen.io/naomihauret/pen/gLvNMw?editors=1010)
* [Codepen Phonebook](https://codepen.io/SG011/pen/xREpNj?editors=0110)
* [Codepen Simple Login](https://codepen.io/WEBteam/pen/KaBdbr?page=7)
* [Codepen more complex Login](https://codepen.io/Apfelbacher/pen/ryqRBQ?page=6)
* [codepen clean login](https://codepen.io/hygorp/pen/wdYrWy)
* [Ui components](https://codepen.io/bsharif/pen/NamqLj?editors=0010)
* [another good data storage](https://codepen.io/iomaismeta/pen/mprgNo?editors=0010)
* [calender ui](https://codepen.io/Darwindeaf/pen/QrzeJN?editors=0010)
* [learnsemantic](http://learnsemantic.com/developing/glossary.html)
* [fomantic-ui brings toaster messages and range sliders and calenders](https://fomantic-ui.com/collections/menu.html)
* [interesting menu](https://codepen.io/mikeair/pen/MYKXPm)
* [Example of change Classes](https://codepen.io/IronGeek/pen/vOejyr)
* [cool dropdown](https://codepen.io/akranjec/pen/pvgXqV)

## Tabset


<!--tabs -->
<!-- <div class="ui grid page"> -->
<!-- <div class="column"> -->
<div class="ui segment">
  <div class="ui menu top">
    <a class="active item" data-tab="edit"><i class="icon edit sign"></i>Edit</a>
    <a class="item" data-tab="summary">Summary</a>
  </div>
  <div class="ui tab" data-tab="edit">
    Hi 1
  </div>
  <div class="ui tab" data-tab="summary">
    H2
  </div>
</div>

<script type="text/javascript">
  $('.top.menu .item').tab();
</script>








<!-- tab context -->
<div class="tab context1">
<!-- tab header -->
<div class="ui secondary menu">
  <div class="active item" data-tab="tab1">Hello 1</div>
  <div class="item" data-tab="tab2">Hello 2</div>
</div>

<!-- tab1 -->
<div class="ui active tab" data-tab="tab1">

Hello 1

</div>

<!-- tab2 -->
<div class="ui tab" data-tab="tab2">

Hello 2

</div>
<!-- tab context -->
</div>

<script type="text/javascript">
$(document)
  .ready(function(){
    $('.tab.context1 .menu .item')
      .tab({
        context: $('.tab.context1')
      });
  });
</script>



## Shape 1


<div class="ui people shape">
<div class="sides">
<div class="side active">
  <div class="ui card">
  <div class="content">

```{r}
print("HAHA1")
```

  <br>
  </div>
  </div>
</div>
<div class="side">
  <div class="ui card">
  <div class="content">

```{r}
print("HAHA2")
```

  <br>
  </div>
  </div>
</div>
<div class="side">
  <div class="ui card">
  <div class="content">
  
```{r}
print("HAHA3")
```

  <br>
  </div>
  </div>
</div>
</div>

<div class="ui blue inverted button" id = "next">Next</div>
<div class="ui green inverted button" id = "back">Back</div>

<script type="text/javascript">
  $(".ui.people.shape").shape();
  $("#next").click(function(e){
    e.preventDefault();
    $(this).closest(".people.shape").shape("flip right")
  });    	
  $("#back").click(function(e){
    e.preventDefault();
    $(this).closest(".people.shape").shape("flip left")
  });
</script>
</div>

## Shape

*[Codepen source code](https://codepen.io/hougasian/pen/oBqQeW)

<br><br>



<div class="ui shape" id = "example2">
  <div class="sides">
    <div class="side active">
      <div class="ui note card">
        <div class="content">
          <div class="ui right corner tiny label">
            <i class="pin icon"></i>
          </div>
          <div class="meta">
            <img class="ui avatar mini image" src="https://avatars2.githubusercontent.com/u/6231956?v=3&s=460">Kevin Hougasian <i class="small yellow calendar outline icon"></i> Feb 2, 2016
          </div>

          <p>While I added this note at some point, I cannot recall its relevancy.</p>
          <p>It's sad really.</p>

          <button class="ui right floated transparent icon button">
            <i class="red trash icon"></i>
          </button>
          <button class="ui right floated transparent icon button">
            <i class="yellow write square icon flip-left"></i>
          </button>

        </div>
      </div>
    </div>
    <div class="side">
      <div class="ui note card edit">
        <div class="content">
          <div class="ui right corner tiny label">
            <i class="pin icon"></i>
          </div>
          <div class="meta">
            <p><img class="ui avatar mini image" src="https://avatars2.githubusercontent.com/u/6231956?v=3&s=460">Kevin Hougasian <i class="small yellow calendar outline icon"></i> Feb 2, 2016</p>
          </div>

          <p>While I added this note at some point, I cannot recall its relevancy.</p>
          <p>It's sad really.</p>

          <button class="ui right floated transparent icon button">
            <i class="red remove icon flip-right"></i>
          </button>

        </div>
      </div>
    </div>
  </div>
</div>

<p class="ui grey header">Click <i class="yellow write square icon"></i>for transition.</p>
<p class="ui grey header">Click <i class="pin icon"></i> to pin.</p>


<script type="text/javascript">
  $('#example2').shape();

  $('.write')
    .on('click', function() {
      $('#example2').shape('flip over');
        var $textarea = $('#example2 textarea'),
        setHeight = $(this)[0].scrollHeight;
        $textarea.height(setHeight).focus();
    });

  $('.remove')
    .on('click', function() {
      $('#example2')
      .shape('flip over');
    });

  // pin
  $('.note.card .corner')
    .on('click', function() {
      $(this)
        .parents('.side')
        .find('.corner')
        .toggleClass('yellow');
    });
</script>


## Calender

<div class="ui calendar" id="example8">
  <div class="ui input left icon">
    <i class="time icon"></i>
    <input type="text" placeholder="Time">
  </div>
</div>

<script type = "text/javascript">
  $(document).ready(function(){
    $('#example8').calendar({
      type: 'year'
    });
  });
</script>

<br/>


## Buttons

<button class="ui labeled icon button">
  <i class="pause icon"></i>
  Pause
</button>
<button class="ui right labeled icon button">
  <i class="right arrow icon"></i>
  Next
</button>


## Data Tables 

* [semantic ui datatable](https://cdn.datatables.net)

```{r results="asis"}
mtcars %>% 
  DT::datatable(., elementId = "mytable")# %>% 
  # shiny::tagList(.) %>% 
  # as.character() %>% 
  # knitr::knit(text = .)
```

<!-- https://datatables.net/examples/styling/semanticui -->
<script type = "text/javascript">
$(document).ready(function() {
  $('#mytable').DataTable();
} );
</script>


## buttons

<div class="treemenu">
  <div class = "ui red segment">
    Hello world
  </div>
</div>

<div class="ui buttons">
  <div class="ui positive button"><i class="codepen icon"></i>  Boxed</div>
  <div class="or"></div>
  <div class="ui button">Non Boxed</div>
</div>


<script type = "text/javascript">
$('.ui.buttons .button').on('click', function() {
  $(this).addClass('positive')
         .siblings()
         .removeClass('positive');
  $('.treemenu').toggleClass('inverted');
});
</script>



<style>
  .blurring.dimmable > :not(.dimmer) {
    filter: @blurredStartFilter;
    transition: @blurredTransition;
  }
</style>

  <!-- $('.segment').dimmer('show'); -->
  <!-- .blurring.dimmed.dimmable > :not(.dimmer) { -->
  <!--   filter: @blurredEndFilter; -->
  <!-- } -->

<!-- https://www.daniweb.com/programming/web-development/code/330933/a-simple-html-login-page-using-javascript -->

## blurred segment login
<div class="ui blurring segment">
  <h3 class="ui header">
  Overlayable Section
  </h3>
  <p>
  <br>
  <br>
  <br>
  <br>
  <br>
  <br>
  <br>
  <br>
  <br>
  <br>
  </p>
  <div class="ui inverted active dimmer" id = "login_dimmer">
  <div class="content">
  <form class = "ui form" name="login">
Username<input type="text" name="userid"/>
Password<input type="password" name="pswrd"/>
<input type="button" onclick="check(this.form)" value="Login"/>
<input type="reset" value="Cancel"/>
</form>
  </div>
  </div>
</div>


<script language="javascript">
$('#login_dimmer').dimmer('show');

function check(form){
 if(form.userid.value == "librarian" && form.pswrd.value == "2018"){
    $('#login_dimmer').dimmer('hide');
    /*$('#login_dimmer').attr({class:'ui dimmer'}); window.open('target.html') opens the target page while Id & password matches*/
  } else {
   alert("Error Password or Username")
  }
}
</script>













<!--menu jabascript -->
<script type = "text/javascript">

//OLD menu JS
// $('.ui.sidebar').sidebar({
//     context: $('.bottom.segment')
//   })
//   .sidebar('attach events', '.menu .item');


$(document).ready(function(){
  //hide the menu
  $("#settings").hide();

  //toggle the menu display  
  $("#menu_link").click(function(){
        $("#settings").slideToggle();
    });

  //if ITU link is clicked then show #itu segment, and
  // hide the #theatre segment
    $("#itu_link").click(function(){
        $("#itu").show();
        $("#theatre").hide();
        insert_data(icu_team);
    });
  
  //if Theatre link is clicked then show #theatre segment, and
  // hide the #itu segment
    $("#theatre_link").click(function(){
        $("#itu").hide();
        $("#theatre").show();
    });
});

</script>







<!-- end -->
</div>
</div>